\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-08 manuscript.Rmd
Analysis flow chart with wokable res

```{r Manuflowchart, include=FALSE }
Flowchart1 <- grViz("digraph nicegraph{

                    graph [fontname = Helvetica,layout = dot,fontsize = 45, ]

@@

                    A[label = '48 items were generated by a robust expert panel'] 
                    B[label = 'Exploratory Factor Analysis on 48 Items (N = 428)']

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
                    fixedsize = true, fontsize = 45]
                    C[label = 
                    <
                    Factor Identification<br align = 'center'/>
                    Scree Plot: 6 Factors<br align = 'center'/>
                    Parallel Analysis: 6 Factors<br align = 'center'/>
                    Minimum Average Partial Method: 5 Factors<br align = 'center'/>
                    Hull Method: 5 Factors<br align = 'center'/>
                    >
                    ]

                     subgraph cluster_1 {
                      graph[fontname = Helvetica, shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
                    fixedsize = true, fontsize = 45]

                     1[label = '5 Factor Solution Retained 25 Items']
                     2[label = 'Reliability Analysis on EFA Sample (N=428)
                    Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62']

                     3[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (25 Items; N=262)
                      Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)']

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52
                      Mcdonald  omega(total) for the total scale = .73']
                    8[label = 'Measurement Invariance Analysis
                    Residual measurement invariance achieved']
                    9[label = 'Semantic Analysis']
                    10[label = 'LEBA Short Form (18 Items; N=690) 
                      Based on Item Response Theory']
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
                fixedsize = true, fontsize = 45 ]
                    6[label = 
                    <
                    6-Factor solution:<br align = 'center'/> 
                    one factor emerged with only two salient loadings
                    >
                    ]
                    7[label = 'Rejected']
                    }

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg')
```

>>>>

```{r Manuflowchart, include=FALSE }
Flowchart1 <- grViz("digraph my_flowchart{

                    graph [fontname = Helvetica,layout = dot,fontsize = 45,layout = dot ]

@@

                    A[label = '48 items were generated'] 
                    B[label = 'Exploratory Factor Analysis on 48 Items (n = 428)']

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
                    fixedsize = true, fontsize = 45]
                    C[label = 
                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Parallel Analysis: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
                    ]

                     subgraph cluster_1 {
                      graph[fontname = Helvetica, shape = box, style =dashed]

                     node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
                    fixedsize = true, fontsize = 45,style =dashed]

                     1[label = '5 Factor Solution Retained 25 Items']
                     2[label = <Reliability Analysis on EFA Sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]

                     3[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (25 Items; n=262)<br/>Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]

                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
                     5[label = <Reliability Analysis on CFA (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
                    8[label = <Measurement Invariance Analysis<br/>Residual measurement invariance achieved>]
                    9[label = 'Semantic Analysis']
                    10[label = <LEBA Short Form (18 Items; n=690)<br/>Based on Item Response Theory>]
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
                fixedsize = true, fontsize = 45 ]
                    6[label = 
                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
                    ]
                    7[label = 'Rejected']
                    }

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg')
```
